R Notebook

### 2020-02-17 src/testing_file.Rmd
building appendix example (bent)

>>>>

#layer join images

```{r}
proj <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
s <- shapefile("../data/plot4-variables/landp/land-wgs84v2.shp")
crs(s) <- proj

temp9 <- raster("../data/env/asciitrim/ascii2004/2004_07_temp.nc_9.82275.asc")
crs(temp9) <- proj
temp221 <- raster("../data/env/asciitrim/ascii2004/2004_07_temp.nc_221.141.asc")
crs(temp221) <- proj
temp508 <- raster("../data/env/asciitrim/ascii2004/2004_07_temp.nc_508.64.asc")
crs(temp508) <- proj

ts <- stack(temp9, temp221, temp508)

levelplot(ts, layout = c(1, 3), scales=list(draw=FALSE), xlab = NULL, ylab = NULL, names.attr = c("", "", ""), colorkey=FALSE, margin = FALSE, par.setting = viridisTheme)
dev.copy(png, (paste0("../output/maxent/paper_plots/temp-example.png")), width = 1080,height = 1920)
dev.off() # stops automatic saving of the plot to a png))

salinity9 <- raster("../data/env/asciitrim/ascii2004/2004_07_salinity.nc_9.82275.asc")
crs(salinity9) <- proj
salinity221 <- raster("../data/env/asciitrim/ascii2004/2004_07_salinity.nc_221.141.asc")
crs(salinity221) <- proj
salinity508 <- raster("../data/env/asciitrim/ascii2004/2004_07_salinity.nc_508.64.asc")
crs(salinity508) <- proj

ts <- stack(salinity9, salinity221, salinity508)

levelplot(ts, layout = c(1, 3), scales=list(draw=FALSE), xlab = NULL, ylab = NULL, names.attr = c("", "", ""), colorkey=FALSE, margin = FALSE, par.setting = viridisTheme)
dev.copy(png, (paste0("../output/maxent/paper_plots/salinity-example.png")), width = 1080,height = 1920)
dev.off() # stops automatic saving of the plot to a png))

```{r}
ras <- raster("../output/maxent/paper_plots/bent_illus/tempmerge.asc")
levelplot(ras, scales=list(draw=FALSE), xlab = NULL, ylab = NULL, names.attr = c(""), colorkey=FALSE, margin = FALSE, par.setting = viridisTheme)
dev.copy(png, (paste0("../output/maxent/paper_plots/bent_illus/temp-concat.png")), width = 1080,height = 1920)
dev.off() # stops automatic saving of the plot to a png))

ras <- raster("../output/maxent/paper_plots/bent_illus/salmerge.asc")
levelplot(ras, scales=list(draw=FALSE), xlab = NULL, ylab = NULL, names.attr = c(""), colorkey=FALSE, margin = FALSE, par.setting = viridisTheme)
dev.copy(png, (paste0("../output/maxent/paper_plots/bent_illus/sal-concat.png")), width = 1080,height = 1920)
dev.off() # stops automatic saving of the plot to a png))
```
